\section{Discussion}
\label{sec:discussion}

In this section, we briefly discuss the ethics of our research and
possible ways to defend against \name attacks.

\subsection{Ethical considerations}
\label{sec:ethics}

Section~\ref{sec:load-freq} discusses how we set up an exit relay to
determine the number of DNS requests per five minute interval.  Since
our exit relay was forwarding traffic of real Tor users, we contacted Princeton
University's institutional review board (IRB) before running the
experiment.  Our IRB deemed that this research did not fall within the
realm of human subjects research.  In addition to contacting our IRB, we
adhered to The Tor Project's ethics guidelines~\cite{ethics-guidelines}.
Specifically, \first we ensured that we only collected data that is safe
to publish, \second we only collected data we needed, and \third we
limited the granularity of the data to minimize the likelihood of
reidentification.  The risk to Tor users of this experiment is negligible.
As for the benefits, by conducting this experiment, we can improve our
understanding of the risks that DNS poses to the anonymity of Tor users
and use this understanding to improve protection for Tor users in the
future.
Thus, we believe that the benefits of our experiment outweigh the risks.

\subsection{Defending against \name attacks}

We now discuss ways to defend against \name attacks.  We distinguish
between short-term solutions that can be implemented quickly
(Section~\ref{sec:short-term}), and long-term solutions that need significantly
more work (Section~\ref{sec:long-term}).

\subsubsection{Short-term solutions}
\label{sec:short-term}

Operators of exit relays face a dilemma: they must either operate their own
resolver, which exposes DNS queries to network adversaries; or, they must use a
third-party DNS resolver, which exposes DNS queries to a third party.  Clearly,
the goal is to minimize exposure of DNS requests, but there are several
dimensions to this.  In lieu of substantial DNS protocol improvements, we can
envision three extreme design points, in which \emph{all} exit relays use \first
Google's DNS resolver; \second their own, local resolver; or \third the resolver
provided by their ISP.  Table~\ref{tab:setup-comparison} summarizes the
important trade-offs for these three setups; the rest of this section discusses
these design points in more detail.  Table~\ref{tab:setup-comparison} shows
three attributes for our hypothetical DNS setups.  ``Network-level Protection''
is achieved if AS-level adversaries cannot easily monitor traffic, ``Avoiding
Centralization'' is achieved if there are many diverse resolvers instead of a
few central ones, and ``Response Quality'' is achieved if DNS responses arrive
quickly and correctly.

\begin{table}[t]
	\renewcommand{\tabcaptext}{A comparison between three design points for DNS
	resolver configuration, assuming all Tor exit relays use the setup in
	question.  Solid black circles are most desirable.}
	\topcap{\tabcaptext}
	\centering
	\begin{tabular}{l c c c}
	\toprule
	\textbf{Setup} &
	\begin{tabular}{@{}c@{}}\textbf{Network-level}\\\textbf{Protection}\end{tabular} &
	\begin{tabular}{@{}c@{}}\textbf{Avoiding}\\\textbf{Centralization}\end{tabular} &
	\begin{tabular}{@{}c@{}}\textbf{Response}\\\textbf{Quality}\end{tabular} \\
	\midrule
	All Google & \RIGHTcircle & \Circle & \CIRCLE \\
	All Local & \Circle & \CIRCLE & \CIRCLE\\
	All ISP & \CIRCLE & \RIGHTcircle & \RIGHTcircle \\
	\bottomrule
	\end{tabular}
	\bottomcap{\tabcaptext}
	\label{tab:setup-comparison}
\end{table}

If all exit relays were to use Google's public resolver, the company would
obtain metadata about the activity of all Tor users, which runs counter to Tor's
design goal of distributing trust.  We clearly should avoid this scenario.
Fifield \ea's~\cite{Fifield2015a} censorship circumvention system meek used to
use Google's cloud infrastructure to tunnel the traffic of censored users up
until May 2016~\cite{meek-shutdown}.  While the system was operational,
thousands of meek clients selected exit relays that use Google's public
resolver, which means that Google saw both traffic entering and, partially,
exiting the Tor network, allowing the company to mount \name attacks.

Next, consider a Tor network that only uses local resolvers.  In this case, Tor
is fully independent of third-party resolvers, at the cost of each iterative DNS
query being exposed to a diverse set of ASes in the network, allowing several
parties to learn the DNS queries of Tor users.

Finally, all exit relays could simply use their ISP-provided resolver.  This
would minimize the network exposure of DNS requests as resolvers are frequently
in the same AS as exit relays, and AS-level adversaries would be unable to
distinguish between DNS requests from exit relays and unrelated ISP customers.
This setup introduces the possibility of misconfigured and censored DNS
resolvers~\cite[\S~4.1]{Winter2014b}.  Besides, just a few ASes---OVH, for
example---host a disproportionate amount of exit relays, turning them into the
centralized data sinks that Tor aims to avoid.

Considering the above, we believe that exit relay operators should avoid public
resolvers such as Google and OpenDNS.  Instead, they should either use the
resolvers provided by their ISP, or run their own, particularly if the
operator's ISP already hosts many other exit relays.  Local resolvers can
further be optimized to minimize information leakage, by (for example) enabling
QNAME minimization~\cite{Bortzmeyer2016a}.

In addition to making recommendations to exit relay operators, we can remotely
influence the cache of each exit relay's resolver.  For example, using {\tt
exitmap}, we can continuously resolve potentially sensitive domains over each
exit relay, right before its TTL is about to expire.  In such a setup, an
attacker gains no advantage from observing DNS traffic from the exit relays
because the domain is always in every exit relay's resolver cache.  This
approach scales poorly, considering the potentially large number of domain names
that would need to be cached (recall that the long tail of unpopular sites are
most vulnerable to \name attacks), but it allows us to eliminate DNS-based
correlation attacks for a select number of sites.

Finally, Tor can fix the Tor clipping bug we discovered and consider
significantly increasing the minimum TTL for the DNS cache at exit relays to
make \name attacks less precise.  This adjustment requires finding the longest
acceptable TTL that does not have a notable negative detriment to user
experience.  Further, as soon as the clipping bug is fixed, website operators
of sensitive websites can opt to increase the TTL of their DNS records.

\subsubsection{Long-term solutions}
\label{sec:long-term}

Additional practical defenses are on the horizon.  Zhu \ea~\cite{Zhu2015a}
proposed T-DNS, which employs several TCP optimizations to transport the DNS
protocol over TLS and TCP.  The TLS layer provides confidentiality between exit
relays and their resolvers.  Finally, site operators whose users are
particularly concerned about safety should offer an onion service as an
alternative.  Facebook, for example, set up {\tt facebookcorewwwi.onion}.  When
connecting to the onion service, Tor users never leave the Tor network, and
hence do not need DNS (as long as the onion service does not embed non-onion
service content).

Deploying defenses against website fingerprinting attacks in Tor should be an
important long-term goal, as well.
Although growing the Tor network will help defend against \name attacks to some
degree, the most important change is to
deploy defenses against these attacks in the first place.  Since \name attacks
significantly increase precision of website fingerprinting attacks, defenses
should be designed to significantly reduce the recall of website fingerprinting
attacks, even when the website fingerprinting attack is configured to sacrifice
precision for recall.
